\documentclass[12pt]{article}

\input{interview/packages}
\input{interview/style}

% You can add an extra speaker using:
% \setspeaker{SpeakerCommand}[Speaker Name] 
% Usage: "\SpeakerCommand This is what they said..." 

\setinterviewee{Nestor}{R}{PenguinOps}{PenguinOps@example.com}

\setinterviewer{Jane}{Doe}{Organisation}{jane@example.com}

\renewcommand{\interviewdate}{\today}

\renewcommand{\interviewcontext}{
    \textbf{Context:} This is a template interview.
}

\renewcommand{\interviewcontent}{
    \Qu Why are you interested in this job and our company?
    \An I was drawn to MSD's direction set out in Te Pae Tawhiti, especially Mana manaaki.
    I value the emphasis on dignity and warmth when working with people. Even in technical
    roles such as a Data Scientist.
    Data science isn't just about numbers; it's about telling stories that improve lives.
    MSD's focus on supporting whānau and our most vulnerable communities really resonates
    with me — especially through Mana manaaki.}

\renewcommand{\interviewcontent}{
    \Qu What are your short-term and long-term goals?
    \An In the short term, I want to bring value to a programme like Te Pae Tawhiti by building 
    trusted, actionable insights. In the long term, I hope to step into a more senior technical
    lead role where I can support joined-up work across government agencies, especially in areas
    impacting social wellbeing.}

\renewcommand{\interviewcontent}{
    \Qu What does teamwork mean to you?
    \An To me, teamwork is about mutual respect, listening, and being open to other perspectives.
     It's also about accountability — doing your part so others can do theirs.
    My best work happens in teams where we're honest, transparent, and united by a shared goal.}

\input{interview/full}
