\section{Work history}
\resumeSubHeadingList
  \resumeSubheading
      {Kaitātari Hoahoa | Design Analyst}{Feb 2023 -- Present}
      {Tautauranga Aotearoa - Stats NZ}{Wellington, NZ}
      \resumeSubHeadingList
          %\resumeItem{\textbullet\ Collaborated across many teams and projects to develop visualization tools, R packages, code project workflows and best-practice version control guidelines.}
          \resumeItem{\textbullet\ Maintained and develop two data portals known as Ngā Tūtohu Aotearoa – Indicators Aotearoa New Zealand and the COVID-19 Data Portal.}
          \resumeItem{\textbullet\ Acted as the administrator of StatsNZ shinyapps.io account: Providing trouble shooting and updating services to over 200 Rshiny apps.}
          \resumeItem{\textbullet\ Acted as the administrator for the StatsNZ public-facing GitHub page.}
          \resumeItem{\textbullet\ Developed interactive dashboard to visualize outcomes for different modelling frameworks for census-related products. One example is the Estimated Resident Population (ERP)}
          
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Climate Database Technician}{Feb 2021 -- Apr 2022}
      {National Instutute of Water and Atmospheric Research}{Wellington, NZ}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Created and R-shiny app to explore the catalogue of weather stations plus their associated error logs, and daily data upload status.}
          \resumeItem{\textbullet\ Improved daily quality control procedures for the network of manual observer weather stations in New Zealand.}
          \resumeItem{\textbullet\ Co-authored the Standard Operating Procedures manual for Climate Data services and SharePoint library}
          \resumeItem{\textbullet\ Delivered Climate data services for more than 10 commercial contracts.}
      \resumeSubHeadingListEnd

   \resumeSubheading
        {Molecular Biologist}{Feb 2016 - Feb 2021}
        {National Instutute of Water and Atmospheric Research}{Wellington, NZ}
    \resumeSubHeadingList
        \resumeItem{\textbullet\ Acquired experience working in a biocontaiment laboatory analyzing genetic data for research. }
        \resumeItem{\textbullet\ Produced hundreds of genetic sequences for the biodiversity programme on marine algae.}
        \resumeItem{\textbullet\ Conducted dissections of Bluff oysters and prepared samples for \textit{Bonamia ostrae} screening.}
    \resumeSubHeadingListEnd

  %  \resumeSubheading
  %      {Biology Professor}{Sep 2014 - Aug 2015}
  %      {}{}
  %  \resumeSubHeadingList
  %      \resumeItem{\textbullet\ Provided theory and laboratory classes up to 40 hours per week as part of the bilingual Biology curriculum.}
  %      \resumeItem{\textbullet\ Consistently achieved monthly and annual department expectations without delays}
  %      \resumeItem{\textbullet\ Mentored a small group of students who obtained high-class awards during the International Biology Olympiads}
  %      \resumeItem{\textbullet\ Participated in the evaluation of the National Biology curriculum.}
  %  \resumeSubHeadingListEnd


    %\resumeSubHeadingListEnd